Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-19 paper.tex
fixing some expresions

\address[ugr]{Department of Computer Architecture and Computer Technology, ETSIIT and CITIC \\
University of Granada, Granada, Spain. Tel: +34958241778. Fax: +34958248993}
\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology \\
The University of Jordan, Amman, Jordan. Tel: +. Fax: +}

@@

It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

@@

The training dataset included historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern. It was provided by the Spanish publishing company Trevenque Editorial S.L.. Table
\ref{tabla:paramsOrig50} shows the initial set of variables describing
each book.

@@

Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. 
% (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
% Antonio - because we should not fill important variables automatically, this adds noise to the data, so I think it is better to remove these patterns, since there are still a lot in the dataset. 
% Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e. \textit{pre-sales data}. Thus, their value do not depend on the book sales. The selected the subset of features is described in Table \ref{tabla:params_pre_sales}.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends, or 
promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. %FERGU: why?
% Antonio - explained.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it in his or her own prediction process.

@@

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}. These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered by a human expert to make predictions.
% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
% Antonio - done
In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?

>>>>

\address[ugr]{Department of Computer Architecture and Computer Technology, ETSIIT and CITIC \\
University of Granada, Granada, Spain. Tel: +34958241778. Fax: +34958248993}
\address[abd]{Business Information Technology Department, King Abdullah II School for Information Technology \\
The University of Jordan, Amman, Jordan}

@@

It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

@@

The training dataset includes historical data about 6083 books published in Spain for several years, with an initial set of 50 variables per pattern. It has been provided by the Spanish publishing company Trevenque Editorial S.L.. Table
\ref{tabla:paramsOrig50} shows the initial set of variables describing
each book.

@@

Starting from these raw data, a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. 
% (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
% Antonio - because we should not fill important variables automatically, this adds noise to the data, so I think it is better to remove these patterns, since there are still a lot in the dataset. 
% Indeed, there were just a couple of patterns without important values, that probably were errors of the extraction process or bad insertions in the database.
Furthermore, the initial set of variables, presented in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to use just those that can be known before a new book is launched, i.e. \textit{pre-sales data}. Thus, their value do not depend on the book sales. The selected subset of features is described in Table \ref{tabla:params_pre_sales}.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends, or 
promotions, that classical prediction methods can not deal with, since they are not included in the dataset due to the difficulty to model them. %FERGU: why?
% Antonio - explained.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it for his or her own prediction process.

@@

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}. These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered by a human expert to make predictions.
% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
% Antonio - done
In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?
